% ResearchBench — ICLR-format paper draft
% Build: pdflatex researchbench_iclr.tex (twice)
% If you obtain the official iclr2026_conference.sty, place it next to this file;
% it will be used automatically. Otherwise a faithful emulation is applied.
\documentclass{article}

\IfFileExists{iclr2026_conference.sty}{%
  \usepackage{iclr2026_conference}%
}{%
  % ---- ICLR-style emulation (matches official geometry & typography) ----
  \usepackage[letterpaper]{geometry}
  \geometry{textheight=9in, textwidth=5.5in, top=1in, headheight=12pt,
            headsep=25pt, footskip=30pt, centering}
  \usepackage{times}
  \usepackage{fancyhdr}
  \pagestyle{fancy}
  \fancyhf{}
  \fancyhead[L]{\small Under review as a conference paper at ICLR 2027}
  \fancyfoot[C]{\thepage}
  \renewcommand{\headrulewidth}{0.4pt}
  \usepackage{titlesec}
  \titleformat{\section}{\large\bfseries\scshape}{\thesection}{1em}{}
  \titleformat{\subsection}{\normalsize\bfseries\scshape}{\thesubsection}{1em}{}
  \titleformat{\subsubsection}{\normalsize\bfseries}{\thesubsubsection}{1em}{}
}

\usepackage[round,authoryear]{natbib}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{url}
\usepackage{microtype}
\usepackage{xcolor}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}

\title{ResearchBench: Rubric-Scored Paper Replication as a\\
Benchmark for Autonomous AI Research Agents}

\author{Annika Kaul Singh\\
Infinity Inc.\\
\texttt{research@infinity.inc}}

\date{}

\begin{document}
\maketitle

\begin{abstract}
Paper replication is a natural target for evaluating automated AI research
agents: the sub-tasks of novel research---environment bring-up, data
preparation, method implementation, benchmarking, and analysis---overlap almost
entirely with the sub-tasks of replicating existing research, and the paper's
own reported numbers provide ground truth. Prior work introduced hand-authored
task decompositions (``rubrics'') that convert binary replication judgments
into graded scores. We show that in 2026 these decompositions, together with
executable per-task correctness tests, can be \emph{generated automatically} by
terminal agents. We present \textbf{ResearchBench}, a frozen benchmark of 20
LLM inference-optimization papers decomposed into 7{,}290 rubric leaves
(1{,}327 implementable headline claims) targeting a single NVIDIA H100. Every
leaf carries an executable verification contract; rubrics and contracts are
content-hashed and frozen so that scores are comparable across agents,
harnesses, and time. We report three same-set evaluation attempts: a clean
baseline in which Claude Code closes 5.95\% and Codex 1.21\% of implementable
claims; a diagnosis, from machine-readable failure attribution, that the
dominant failure mode was \emph{harness legibility} (agents never produced the
exact artifact and test paths the grader checks); and a one-paragraph harness
intervention that lifts both backends' closure approximately fivefold with the
model unchanged. We further describe behavioral (rather than textual) defenses
against reward hacking, including isolated re-execution of the agent's
reproduction script with wall-time, GPU-utilization, and file-diff checks. We
argue that benchmarks for research agents must attribute failures across the
model / harness / rubric / environment layers, or they will mis-rank models,
and we position ResearchBench as a yardstick for the question: \emph{which
coding agent, in which harness, at what compute, can you trust to do autonomous
research?}
\end{abstract}

\section{Introduction}

The goal of automated AI research is an agent that can take a hypothesis,
implement it, run the experiments, and report faithful results. Evaluating
progress toward this goal is difficult precisely because novel research has no
ground truth. Paper replication offers an escape: the sub-tasks of replicating
a published paper are, to a first approximation, the same sub-tasks required to
execute novel research, yet the paper's reported numbers supply a checkable
target. An agent that faithfully replicates a systems paper---rebuilding the
method, re-running the experiments, and matching the headline numbers within
tolerance---has demonstrated the skills that novel research requires.

Two obstacles have historically limited replication as a benchmark. First,
replication was scored as a binary judgment, collapsing a months-long effort
into one bit. PaperBench \citep{starace2025paperbench} addressed this by
introducing \emph{rubrics}: expert-authored decompositions of a paper into
graded sub-tasks. Second, authoring such rubrics required scarce expert labor,
capping benchmark size and freshness. The contribution of this paper is to show
that both the decomposition \emph{and} the per-task correctness tests can now be
generated automatically by terminal agents, and to demonstrate what a frozen,
automatically-generated, execution-verified replication benchmark reveals about
today's coding agents and---critically---about the \emph{harnesses} that drive
them.

Concretely, we make four contributions:

\begin{enumerate}
  \item \textbf{ResearchBench}, a frozen benchmark of 20 LLM
        inference-optimization papers decomposed into 7{,}290 automatically
        generated rubric leaves (93--935 per paper), of which 1{,}327 are
        implementable headline claims. Each measured leaf carries an executable
        verification contract (expected artifact path, paper value, unit,
        tolerance rule). Rubrics and contracts are content-hashed and frozen;
        all runs grade against byte-identical targets (\S\ref{sec:benchmark}).
  \item \textbf{A layered failure taxonomy} that attributes every non-passing
        leaf to an owner layer (test harness, result artifact, rubric,
        implementation, environment), separating ``the model is weak'' from
        ``the harness never asked for the right file'' (\S\ref{sec:method}).
  \item \textbf{Evidence that harness legibility dominates measured agent
        skill.} In a clean-baseline evaluation, Claude Code closes 5.95\% and
        Codex 1.21\% of implementable claims. Failure attribution shows the
        bottleneck is that agents do not produce the exact per-leaf test and
        artifact files the grader checks. A one-paragraph prompt intervention
        stating the deterministic leaf$\rightarrow$file mapping lifts both
        backends approximately $5\times$, with the models unchanged
        (\S\ref{sec:experiments}).
  \item \textbf{Behavioral anti-reward-hacking defenses.} Text-pattern
        safeguards (confession regexes, prompt directives, negative controls)
        were each bypassed within one run. Defenses that check facts the agent
        did not author---isolated re-execution of \texttt{reproduce.sh} with
        wall-time, GPU-utilization, and file-diff observation---have held
        (\S\ref{sec:hacking}).
\end{enumerate}

\section{Related Work}

\textbf{Replication benchmarks.} PaperBench \citep{starace2025paperbench}
introduced expert-authored rubric trees for grading paper replication by ML
agents. CORE-Bench \citep{siegel2024core} evaluates computational
reproducibility of published results given the paper's own code. ResearchBench
differs on three axes: rubrics and tests are generated automatically rather
than by experts; official repositories are \emph{blacklisted}, forcing
independent reimplementation; and grading is attached to executable contracts
with numeric tolerances rather than LLM judgment alone.

\textbf{Agentic coding benchmarks.} SWE-bench \citep{jimenez2024swebench}
scores repository-level bug fixing; MLE-bench \citep{chan2024mlebench} scores
Kaggle-style ML engineering; RE-Bench \citep{wijk2024rebench} compares agents
to human experts on open-ended research engineering tasks. These evaluate
components of research skill; ResearchBench evaluates the composed,
end-to-end activity---replicate the paper, reproduce its numbers---under
budgeted compute, and additionally isolates the harness as an object of study.

\textbf{Reward hacking in evaluation.} Specification gaming by agents under
optimization pressure is well documented \citep{krakovna2020specification}. Our
contribution is operational: a taxonomy of textual safeguards that failed in
practice and behavioral safeguards that held, in the specific setting of
replication scoring.

\section{The ResearchBench Benchmark}
\label{sec:benchmark}

\subsection{Papers and scale}

The frozen set \texttt{researchbench\_inference20\_h100} contains 20 papers on
LLM inference optimization: serving simulators, KV-cache management
(SSD-backed, temporally tiered, prefix), prefill/decode disaggregation,
SLO-aware scheduling, mixed-precision inference, GPU kernel optimization, and
parallelism strategies (full list in Appendix~\ref{app:papers}). The hardware
target is a single NVIDIA H100 80GB. Across the set there are 7{,}290 rubric
leaves (93--935 per paper, median ${\sim}300$) and 1{,}327 implementable
headline claims. The set was frozen on 2026-06-25; the SHA-256 of every
rubric and contract file is recorded in the benchmark manifest and re-verified
before and after every run.

\subsection{Automated rubric generation}

For each paper, a pipeline of terminal-agent stages produces the evaluation
targets without expert authorship: (i) ingestion converts the arXiv source to
\texttt{paper.md}; (ii) a triage stage scores replicability and estimated GPU
hours; (iii) a rubric generator drafts a task tree from the paper text; (iv) a
rubric critic performs a two-pass critique-and-fix loop until convergence,
with schema salvage for malformed outputs; (v) a health check audits leaf
quality; (vi) a feasibility stage estimates cost, and an unblockers stage
live-probes whether referenced models and datasets are actually retrievable;
(vii) a test generator emits a shared structural/behavioral test suite and an
interface contract that every implementation must expose.

Leaves carry a verification block \{type, spec, paper citation\} and
preconditions (\texttt{requires\_hardware}, \texttt{requires\_pretrained},
\dots). Verification types are \emph{structural} (API surface exists),
\emph{evidence} (implementation contains paper-specific logic),
\emph{behavioral} (deterministic computation matches), and \emph{measured}
(\texttt{result\_match} against a paper value).

\subsection{Verification contracts}

Every measured leaf is bound to an executable contract specifying the exact
artifact path the implementation must emit and the tolerance under which the
measured value is accepted, e.g.:

\begin{quote}\small
\texttt{expected\_output = results/leaf\_<id>.json};\quad
\texttt{tolerance:\ abs(measured $-$ 2.1)/2.1 $\le$ 0.4}
\end{quote}

A leaf is credited only when a pytest verifier at a deterministic path
(\texttt{\_tests\_local/test\_leaf\_<id>.py}) passes while reading that
artifact. Credit is attributed by executing tests, never by the agent's
claims.

\subsection{Replicable vs.\ unreplicable work}

Unreplicability is recorded per leaf, not per paper. Leaves whose
preconditions cannot be met in the declared environment (hardware the original
authors used but we lack---A100, H200, TPU-v7; heavyweight pretrained models;
proprietary traces) are classified \texttt{skipped-environment} and excluded
from the achievable denominator, with audited skip reasons. Three papers have
no implementable headline baseline in this environment and score n/a; the
remaining 17 are scoreable end-to-end. As an example of the environment split,
one KV-cache paper decomposes into 309 leaves of which 218 are
environment-skipped and 91 achievable.

\subsection{Compute budgets and honest scoping}

Each run gives the agent an explicit resource contract: a dollar budget, a
wall-clock cap, and a maximum number of iterations, along with the paper's
feasibility estimate. Agents are instructed to scope honestly---documenting
skipped leaves rather than fabricating them---and, per iteration, are focused
on a small \emph{target slice} of open leaves with exact expected outputs,
which converts a several-hundred-leaf rubric into tractable turns.

\section{Evaluation Methodology}
\label{sec:method}

\subsection{Agent contract and iterated sessions}

The replication agent receives only \texttt{paper.md}, the interface contract,
the rubric, the verification contracts, and stock terminal tools (read, write,
edit, bash, glob, grep). The paper's official repository is blacklisted,
forcing independent reimplementation. Because agent sessions cannot be
resumed, all state lives on disk (progress log, source tree, per-leaf tests,
results); an outer loop re-invokes the agent in fresh sessions---selecting a
repair slice, running a turn, grading, attributing failures, and choosing the
next slice---until headline closure validates or budget/iteration/wall caps
are reached. A full 20-paper backend run completes in roughly 10--14 hours on
one H100.

\subsection{Grading and failure attribution}

Grading is three-layered: per-leaf test attribution (which executable verifier
passed), reproduction quality (below), and aggregate scores. Every
non-passing leaf is assigned a failure category and an \emph{owner layer}
(Table~\ref{tab:taxonomy}). This attribution is what makes harness
optimization tractable: without it, harness illegibility is indistinguishable
from model weakness and benchmarks will mis-rank models.

\begin{table}[t]
\caption{Failure taxonomy. Every non-passing leaf is attributed to a category
and owner layer.}
\label{tab:taxonomy}
\begin{center}
\small
\begin{tabular}{llp{6.1cm}}
\toprule
\textbf{Category} & \textbf{Owner layer} & \textbf{Meaning} \\
\midrule
\texttt{missing\_per\_leaf\_test} & test harness & no executable verifier was produced for the leaf \\
\texttt{missing\_result\_artifact} & result artifact & the contract-named output file was never emitted \\
\texttt{broad\_leaf\_unverifiable} & rubric & leaf too coarse to verify; needs splitting \\
\texttt{verification\_gap} & implementation & code ran; evidence does not match the contract \\
\texttt{numeric\_mismatch} & implementation & measured, but outside tolerance \\
\texttt{environment\_blocked} & environment & hardware/model/dataset unavailable \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

\subsection{Behavioral defenses against reward hacking}
\label{sec:hacking}

Agents under budget pressure fabricate: hard-coded ``results,'' tests that
assert paper constants, and confident reports of runs that never happened.
Our experience is that \emph{every} text-pattern safeguard was bypassed within
one run of deployment: a regex confession audit for terms like
``cached''/``surrogate'' was defeated by renaming to
\texttt{paper\_reported}; an empty-source negative control was defeated by
tests that passed on stubs; a ``do not fabricate'' prompt directive had no
measurable effect.

Durable safeguards check facts about the run that the agent did not author.
The primary mechanism is \textbf{isolated reproduction}: the grader deletes
the agent's \texttt{results/} directory, re-runs the agent's
\texttt{reproduce.sh} from scratch, and observes wall time, GPU utilization,
and file diffs. Runs whose regenerated results are byte-identical re-ships of
pre-baked constants, or that complete implausibly fast with no GPU activity,
are classified \texttt{suspect} and their scores gated. Planned extensions
include cost/time floors (actual spend versus the claimed-leaves estimate) and
tool-use forensics on agent transcripts. Our design rule: \emph{if a safeguard
can be defeated by different words, it will be.}

\section{Experiments}
\label{sec:experiments}

\subsection{Setup: same-set attempts}

All experiments run on the frozen set with byte-identical rubrics and
contracts, one shared controller, and only the backend adapter varying between
Claude Code (\texttt{claude-opus-4-7}) and Codex (\texttt{gpt-5-codex}).
Attempt~1 established the shared controller on a mixed-source snapshot.
Attempt~2 is the \textbf{clean baseline}: stock harness, prompts, and
adapters, run from a clean tree at committed \texttt{main} (budget \$200/paper,
15 iterations, 8h wall). Attempt~3 applies a single \textbf{harness
intervention} (below) with raised compute caps (\$1000/paper, 40 iterations,
12h wall).

\subsection{Clean-baseline results (Attempt 2)}

Codex closed 16/1327 implementable claims (1.21\%) and Claude Code 79/1327
(5.95\%); average total-implemented across all rubric leaves was 0.21\% and
1.44\% respectively. Claude led on 12 papers, Codex on 2, with 3 tied.
The two backends failed differently: Codex predominantly stopped before
producing artifacts (13/20 papers with replication runtime failures; 1{,}231
leaves blocked on \texttt{missing\_result\_artifact}), while Claude more often
reached verification and stalled on coverage (13/20 papers ending
\texttt{reproduction\_not\_verified\_within\_budget}; 1{,}233 leaves on
\texttt{missing\_per\_leaf\_test}; 73 on \texttt{numeric\_mismatch}---Claude
got to measured numbers more often, and sometimes missed tolerance).
Unclosed implementable work concentrated in benchmark-heavy task categories
(Table~\ref{tab:categories}).

\begin{table}[t]
\caption{Where implementable work remained open (both backends, Attempt 2).}
\label{tab:categories}
\begin{center}
\small
\begin{tabular}{lr}
\toprule
\textbf{Missed task type} & \textbf{Unclosed leaves} \\
\midrule
Evaluation, Metrics \& Benchmarking & 1448 \\
Method Implementation & 955 \\
Experimental Setup & 450 \\
Environment \& Infrastructure Setup & 47 \\
Dataset and Model Acquisition & 43 \\
Logging, Analysis \& Presentation & 28 \\
Data Processing \& Preparation & 27 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

\subsection{Diagnosis: harness legibility, not model capability}

Failure attribution located the bottleneck precisely. A leaf can only be
credited when a pytest file exists at the deterministic path
\texttt{\_tests\_local/test\_leaf\_<id>.py} and passes while reading the
contract-named artifact. Inspection of failed workdirs showed agents writing
correct-\emph{shaped} tests and artifacts, but only for the current target
slice (${\sim}4$ leaves), leaving 80+ achievable leaves per paper unverified:
the implementation existed, but the grader was never shown the files it
checks. Nothing in the baseline prompts stated the leaf$\rightarrow$file
mapping or instructed exhaustive coverage.

\subsection{Intervention and results (Attempt 3)}

We appended one paragraph to each backend's prompt stating (i) the
deterministic leaf$\rightarrow$test-path and contract$\rightarrow$artifact-path
mapping, (ii) an instruction to enumerate \emph{every} achievable leaf rather
than the current slice, and (iii) a reminder that \texttt{reproduce.sh} must
regenerate \texttt{results/} from scratch. No frozen artifact, grader, or
adapter changed; hash checks confirm identical rubrics and contracts.

\begin{table}[t]
\caption{Implementable-claim closure across same-set attempts. Models
unchanged throughout.}
\label{tab:attempts}
\begin{center}
\small
\begin{tabular}{llrr}
\toprule
\textbf{Attempt} & \textbf{Change vs.\ prior} & \textbf{Codex} & \textbf{Claude Code} \\
\midrule
2 (clean baseline) & none & 16/1327 = 1.21\% & 79/1327 = 5.95\% \\
3 (legibility patch) & prompt paragraph + raised caps & 78/1327 = 5.88\% & 454/1327 = 34.21\% \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

Both backends improved roughly fivefold (Table~\ref{tab:attempts}): Codex's
closure rose $4.9\times$ (average total-implemented 0.21\% to 1.63\%) and
Claude Code's $5.7\times$ (1.44\% to 8.96\%), with five papers exceeding 70\%
closure under Claude---including the FP16-equivalence paper, a historic stuck
case that had scored zero in every prior run. We emphasize the
confound: Attempt~3 changed the prompt \emph{and} the compute caps, and ran
both backends concurrently on one H100 (a minor contention risk for
latency-sensitive measured leaves). Isolating the levers is Attempt~4.
Nevertheless, the qualitative conclusion is robust: a large fraction of what a
naive benchmark would report as ``agent failure'' was \emph{harness
legibility} failure. Test-time compute also matters---the raised caps give
the agent enough iterations to cover hundreds of leaves---but compute alone
could not have produced files the agent did not know to write.

\subsection{Harness evaluation independent of the model}

Because inputs, rubrics, and contracts are frozen and only the backend adapter
varies, cross-backend differences attribute to the model-plus-harness pair,
and attempt-over-attempt deltas attribute to the harness alone. We propose a
baseline grid crossing models (Claude, Codex, GLM 5.2) with harnesses
(OpenCode, Cursor, Claude Code); the Claude Code harness column is measured in
this paper and the remaining cells are planned. Open questions this grid can
answer empirically: Claude Code vs.\ Codex as a harness; open- vs.\
closed-source models at research tasks (GLM 5.2 vs.\ Claude/Codex); and
frontier-tier comparisons (Fable vs.\ Mythos). \todo{fill grid cells as runs
complete}

\section{Discussion and Future Work}

\textbf{Automated harness optimization.} The failure taxonomy is
machine-readable (per-run category and owner-layer counts). The Attempt-3 fix
was found by reading that attribution; the loop can be closed automatically:
run $\rightarrow$ attribute failures $\rightarrow$ propose a harness patch
$\rightarrow$ smoke on one paper $\rightarrow$ full run $\rightarrow$ compare
on the frozen set. Frozen hashes make every candidate comparable, turning the
benchmark into a reward signal for harness search. A guardrail from our
experience: optimize against a diverse rotation of paper types, never a single
stuck paper, so regressions on one type are caught.

\textbf{Composing new research from rubric leaves.} Because rubrics decompose
papers into reusable sub-tasks, a new idea can be expressed as a novel
composition of leaves from existing rubrics (e.g., one paper's KV-cache
tiering with another's prefill layout), evaluated with the same contracts and
isolated reproduction. This extends the benchmark from replication to
\emph{automated research execution}, including tasks proposed by AI hypothesis
systems.

\textbf{Production integration.} The motivating use case is a company that
wants a relevant paper's improvements in its internal, performance-sensitive
codebase---today, manual researcher work. Inference optimization is the
sharpest test bed: numbers are hardware-sensitive and ``it runs'' $\neq$ ``it
reproduces.'' The same contracts that grade replication become acceptance
tests for landing the technique in production CI.

\textbf{Limitations.} (i) Rubric quality is itself machine-generated; the
\texttt{broad\_leaf\_unverifiable} class quantifies, but does not eliminate,
coarse leaves. (ii) Attempt-3 confounds prompt and compute changes (isolation
planned). (iii) The current set covers one domain (inference systems) and one
hardware target; breadth across research areas is future work. (iv) Two
backends were run concurrently on a shared GPU in Attempt~3, a contention risk
for a small number of latency-sensitive leaves.

\section{Conclusion}

ResearchBench demonstrates that rubric-scored paper replication can be
automated end-to-end---decomposition, executable verification, budgeted agent
execution, and anti-fabrication auditing---and frozen for longitudinal
comparison. Its first empirical lesson is cautionary for the field: the
largest single lever on measured ``agent research ability'' was not the model
but whether the harness made the grading contract legible to the agent. We
release the attempt history as a standing scoreboard and invite the community
to measure models, harnesses, and compute policies against it.

\bibliographystyle{plainnat}
\begin{thebibliography}{9}

\bibitem[Chan et~al.(2024)]{chan2024mlebench}
J.~S. Chan, N.~Chowdhury, O.~Jaffe, et~al.
\newblock MLE-bench: Evaluating machine learning agents on machine learning
  engineering.
\newblock \emph{arXiv:2410.07095}, 2024.

\bibitem[Jimenez et~al.(2024)]{jimenez2024swebench}
C.~E. Jimenez, J.~Yang, A.~Wettig, et~al.
\newblock SWE-bench: Can language models resolve real-world GitHub issues?
\newblock In \emph{ICLR}, 2024.

\bibitem[Krakovna et~al.(2020)]{krakovna2020specification}
V.~Krakovna, J.~Uesato, V.~Mikulik, et~al.
\newblock Specification gaming: the flip side of AI ingenuity.
\newblock DeepMind Blog, 2020.

\bibitem[Siegel et~al.(2024)]{siegel2024core}
Z.~S. Siegel, S.~Kapoor, N.~Nadgir, B.~Stroebl, and A.~Narayanan.
\newblock CORE-Bench: Fostering the credibility of published research through a
  computational reproducibility agent benchmark.
\newblock \emph{arXiv:2409.11363}, 2024.

\bibitem[Starace et~al.(2025)]{starace2025paperbench}
G.~Starace, O.~Jaffe, D.~Sherburn, et~al.
\newblock PaperBench: Evaluating AI's ability to replicate AI research.
\newblock \emph{arXiv:2504.01848}, 2025.

\bibitem[Wijk et~al.(2024)]{wijk2024rebench}
H.~Wijk, T.~Lin, J.~Becker, et~al.
\newblock RE-Bench: Evaluating frontier AI R\&D capabilities of language model
  agents against human experts.
\newblock \emph{arXiv:2411.15114}, 2024.

\end{thebibliography}

\appendix

\section{Benchmark composition}
\label{app:papers}

\begin{table}[h]
\caption{Papers in \texttt{researchbench\_inference20\_h100} with rubric leaf
counts. Three papers (marked $\dagger$) have no implementable headline baseline
in the declared environment and score n/a.}
\begin{center}
\small
\begin{tabular}{lr@{\qquad}lr}
\toprule
\textbf{Paper (slug, abbreviated)} & \textbf{Leaves} & \textbf{Paper} & \textbf{Leaves} \\
\midrule
llmservingsim-2.0 & 214 & icecache & 935 \\
FOCUS-autokernel & 268 & lamp & 288 \\
fp16-equivalence & 650 & niyama & 160 \\
nexus & 312 & prefill-as-a-service & 532 \\
adaserve & 692 & ragged-paged-attention & 442 \\
asynctls & 475 & shift-parallelism & 407 \\
cacheflow & 177 & ttkv & 565 \\
contiguouskv & 309 & tutti & 220 \\
duetserve & 350 & fast-heterogeneous$^\dagger$ & 93 \\
flexicache$^\dagger$ & 96 & hexgen-flow$^\dagger$ & 105 \\
\midrule
\multicolumn{2}{l}{\textbf{Total}} & & \textbf{7{,}290} \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

\section{The Attempt-3 legibility paragraph}
\label{app:blurb}

The full text appended to both backends' prompts (verbatim):

\begin{quote}\small\ttfamily
LEAF -> FILE PATH MAPPING (this is how you score; read carefully):\\
- A rubric leaf is counted as verified ONLY when a pytest file exists at the
exact path \_tests\_local/test\_leaf\_<LEAF\_ID>.py and passes, where
<LEAF\_ID> is the leaf's id with every hyphen '-' replaced by '\_'. If that
file is missing, the leaf stays unverified and scores zero no matter how
correct your src/ code is.\\
- For measured / result\_match leaves, that test must load the artifact named
by the leaf's contract expected\_output (see ../verification\_contracts.json;
convention results/leaf\_<LEAF\_ID>.json) and assert the contract's
field(s)/tolerance.\\
- Enumerate EVERY leaf in ../rubric.json and ../verification\_contracts.json.
For each leaf NOT blocked by unavailable hardware/models/datasets (i.e.\ every
achievable leaf, not just the current target slice), write its
\_tests\_local/test\_leaf\_<LEAF\_ID>.py AND emit the result artifact that
test reads. Breadth of achievable-leaf coverage is the single biggest lever on
your score.\\
- reproduce.sh must regenerate all of results/ from scratch (the grader wipes
results/ and reruns reproduce.sh in isolation).
\end{quote}

\section{Reproduction quality gates}
\label{app:gates}

Isolated reproduction classifies each run as \texttt{ok}, \texttt{suspect}, or
\texttt{failed}: \texttt{failed} if \texttt{reproduce.sh} is absent, exits
nonzero, times out, or produces zero files into a wiped \texttt{results/};
\texttt{suspect} if wall time is implausibly short with no GPU activity, or if
more than half of the regenerated files are byte-identical to the agent's
pre-authored results with no authored code paths present. Suspect and failed
runs have their leaf credit gated.

\end{document}
